---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# NPV

<!-- badges: start -->
<!-- badges: end -->

NPV represents an economic concept known as net present value. The goal of the 
function is to allow the user to calculate the total NPV from consecutive yearly
profits, as well as a discount rate based on the user's adopted methodology 
(i.e. conventional, intergenerational). To learn more about net present values, 
you can access the website [here](https://www.investopedia.com/terms/n/npv.asp#:~:text=Net%20present%20value%20(NPV)%20is,a%20projected%20investment%20or%20project.).

## Installation

You can install the released version of NPV from github with:

``` r
devtools::install_github("amejaes/NPV")
```
## Creating the Function

To create the function, I first started with the simple NPV calculation, which is:

(y+1)^x

In this equation, y is the discount rate and x represents the yearly profit. 

Next, I knew that I needed to include a loop, so that we could calculate the NPV over multiple years. To do so, I decided to employ the purrr function, map2_dbl. Finally, I used sum() to determine the total NPV, regardless of the number of years of data that are calculated. 

```{r}
NPV <- function(x, y) {
  if(length(y) > 1) {
    stop('I am so sorry, but this function only works when the number of elements in y is 1.')
  }
  sum(purrr::map2_dbl(x, y, ~(.y+1)^.x))
}
```

In addition, the if statement was included to prevent the user from trying to input more than one element as the discount rate.

## Inputs

Below are the inputs that the NPV function requires:

- `x`: A numeric vector that may consist of one or more elements. This input 
represents the yearly profits in a consecutive fashion. 
- `y`: A numeric vector that only consists of one elements. This input 
represents the discount rate and generally is a value between 0 and 1. 

## Example

Here is a basic example which shows you how to calculate the NPV if you have 
yearly profits of 1500, 2200, and 1800, respectively, and you would like to use
a conventional discount rate of 5.8%:

```{r example}
library(NPV)
NPV(c(1500, 2200, 1800), 0.058)
```

Please see the vignette for additional examples.

## Creating the Package

1. To create the package, I loaded devtools() before using create_package("~/Desktop/NPV") to create a package for my function locally.

2. use_git() was run and the files were committed to activate the Git pane. 

3. While DESCRIPTION and NAMESPACE are both created with create_package(), the function's R document was created using use_r("NPV"), and the README and vignette files were created and built using use_readme_rmd(), build_readme(), use_vignette("Calculating_NPVs"), and build_vignettes(). Both the README file and the vignette were manually configured and written. 

4. The DESCRIPTION was filled in manually as well as using devtools, such as use_mit_license("Annie Mejaes") and use_packages("purrr").

5. To run tests, I used use_testthat() followed by use_test("NPV") to create a test file for my function.Then, I manually created the tests. 
